importE2data

### 2018-02-27 E1/importE1data.Rmd
starting to mixture model

#First experiment of second backwards-letters paper. random orientation each trial.
rawDataPath<- file.path("~",GoogleDrivePath,
                            "E1/Data/RawData/Data")
#raw data path containing .mat file for each subject
rawDataExcludedByMATLABpath<- file.path(rawDataPath, "Excluded")

@@

  files <- dir(path=rawDataPath,pattern='.mat')  #find all data files in this directory
  dfAll<-data.frame()
  for (i in 1:length(files)) { #read in each file
    fileThis<- file.path(rawDataPath,files[i])
    rawDataLoad=tryCatch(
      readMat(fileThis),
      error=function(e) {
        stop( paste0("ERROR reading the file ",fname," :",e) )
      } )
    apparentSubjectName <- strsplit(files[i],split="_")[[1]][1]
    subjectName<- rawDataLoad$participantID[[1]]
    if (apparentSubjectName != subjectName) {
      stop( paste0("WARNING apparentSubjectName",apparentSubjectName," from filename does not match subjectName in data structure",subjectName) )
    }
    rawDataLoad$file <- files[i]

@@

```{r sanity visual check}

sanityVisualCheck<-TRUE
if (sanityVisualCheck) {
  library(ggplot2)
  g=ggplot(excluded, aes(x=SPE))
  #plot data
  g<-g+geom_histogram(binwidth=1)
  g
}

@@

#Meaning of condition variable
#1 - upright
#2 - inverted

@@

#save dataframe into proper library data directory
save(backwards2_E1, file = "data/backwards2_E1.rda", compress="bzip2")

>>>>

#First experiment of second backwards-letters paper. random orientation each trial.
rawDataPath<- file.path(GoogleDrivePath,
                            "Data/RawData/Data")
#raw data path containing .mat file for each subject
rawDataExcludedByMATLABpath<- file.path(rawDataPath, "Excluded")

@@

  files <- dir(path=rawDataPath,pattern='.mat')  #find all data files in this directory
  dfAll<-data.frame()
  for (i in 1:length(files)) { #read in each file
    fileThis<- file.path(rawDataPath,files[i])
    rawDataLoad=tryCatch(
      readMat(fileThis),
      error=function(e) {
        stop( paste0("ERROR reading the file ",fileThis," :",e) )
      } )
    apparentSubjectName <- strsplit(files[i],split="_")[[1]][1]
    subjectName<- rawDataLoad$participantID[[1]]
    if (apparentSubjectName != subjectName) {
      stop( paste0("WARNING apparentSubjectName",apparentSubjectName," from filename does not match subjectName in data structure",subjectName) )
    }
    rawDataLoad$file <- files[i]

@@

Sanity visual check that see histogram.
```{r sanity visual check}

sanityVisualCheck<-TRUE
if (sanityVisualCheck) {
  library(ggplot2)
  g=ggplot(excluded, aes(x=SPE))
  #plot data
  g<-g+geom_histogram(binwidth=1)
  show(g)

  h<-ggplot(E,aes(x=SPE)) + geom_histogram(binwidth=1)
  show(h)
}

@@

Meaning of condition variable
* 1 - upright
* 2 - inverted

@@

#save dataframe into proper library data directory
#save(backwards2_E1, file = "data/backwards2E1_rawDataFromMAT.rda", compress="bzip2")
saveRDS(backwards2_E1, file = "Data/backwards2E1_rawDataFromMAT.rda", compress="bzip2")
```
